# Introduction

This report analyses the **Emotion Twister Survey** for **`{r} company_name`**, covering **`{r} period_cover_lab`**. `{r} data_source_lab`

Instruments:

- **WHO-5 Well-Being Index** (Part 1) — 5 items scored 0–5; total **0–25**. Higher scores indicate better emotional wellbeing. Categories use the **clinical screening cutoff**: Poor wellbeing (raw score ≤13) versus Adequate wellbeing (14–25).
- **Harvard Thriving from Work Questionnaire (TfWQ) short form** (Part 2 items 3–10) — collected on a 5-point agreement scale (total **8–40**). For US-normed interpretation the sum is linearly rescaled to the official 1–6 metric (**8–48**) and converted to a **T-score** (US validation mean 50, SD 10). T < 50 is below the US average; T ≥ 50 is at or above it.
- Item-level analysis focuses on TfWQ survey items **4, 5, 6, 9, and 10** (original 1–5 responses).
- A **descriptive 2 × 2 category matrix** (not LPA) crosses WHO-5 Poor (≤13) vs Adequate (14–25) with TfWQ T < 50 vs T ≥ 50. A **joint latent profile analysis** then models WHO-5 and the US-normed TfWQ T-score in one mixture, with the number of classes chosen from the data rather than forced to 2 × 2.
- **Section 7** runs a second LPA on **all scored item responses** (WHO-5 items 1–5, peer support items 1–2, and TfWQ items 3–10), not the two scale totals.

Every results table can be downloaded as CSV or Excel. A combined workbook is at the end of the report.

# Load packages and data

```{r}
#| label: load-packages

library(httr2)
library(jsonlite)
library(tidyverse)
library(scales)
library(knitr)
library(ggplot2)
library(DT)
library(htmltools)
library(writexl)
library(mclust)
library(readxl)
```

```{r}
#| label: helpers

.table_store <- list()

src_cap <- function() {
  sprintf(
    "Source: Emotion Twister Survey · %s · %s – %s",
    company_name,
    format(start_date, "%d %b %Y"),
    format(end_date, "%d %b %Y")
  )
}

theme_report <- function() {
  theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 13),
      plot.caption = element_text(size = 8, colour = "grey40"),
      panel.grid.minor = element_blank()
    )
}

show_tbl <- function(data, id, caption = NULL) {
  stopifnot(is.data.frame(data), nchar(id) > 0)
  .table_store[[id]] <<- data

  csv_txt <- paste(capture.output(write.csv(data, row.names = FALSE, na = "")), collapse = "\n")
  csv_b64 <- jsonlite::base64_enc(charToRaw(enc2utf8(csv_txt)))

  htmltools::tagList(
    if (!is.null(caption)) htmltools::tags$p(htmltools::tags$strong(caption)),
    htmltools::tags$p(
      htmltools::tags$a(
        href = paste0("data:text/csv;charset=utf-8;base64,", csv_b64),
        download = paste0(id, ".csv"),
        class = "btn-dl",
        "Download CSV"
      )
    ),
    htmltools::div(
      class = "report-table",
      DT::datatable(
        data,
        rownames = FALSE,
        width = "100%",
        fillContainer = FALSE,
        class = "display compact",
        options = list(
          pageLength = 12,
          scrollX = FALSE,
          autoWidth = FALSE,
          searching = nrow(data) > 12,
          paging = nrow(data) > 12,
          info = nrow(data) > 12,
          dom = if (nrow(data) > 12) "ftip" else "t"
        )
      )
    )
  )
}

mean_by_group <- function(data, group, score) {
  data |>
    filter(!is.na({{ group }}), !is.na({{ score }})) |>
    group_by({{ group }}) |>
    summarise(
      n = n(),
      mean = mean({{ score }}),
      sd = sd({{ score }}),
      median = median({{ score }}),
      se = if_else(n() > 1, sd({{ score }}) / sqrt(n()), NA_real_),
      .groups = "drop"
    ) |>
    mutate(
      mean = round(mean, 2),
      sd = round(sd, 2),
      median = round(median, 2),
      se = round(se, 2)
    )
}

cat_by_group <- function(data, group, cat) {
  data |>
    filter(!is.na({{ group }}), !is.na({{ cat }})) |>
    count({{ group }}, {{ cat }}, name = "n") |>
    group_by({{ group }}) |>
    mutate(
      group_n = sum(n),
      pct = round(100 * n / group_n, 1)
    ) |>
    ungroup()
}

lpa_entropy <- function(z) {
  if (is.null(z)) return(NA_real_)
  k <- ncol(z)
  if (k < 2) return(1)
  z <- pmin(pmax(as.matrix(z), 1e-12), 1)
  n <- nrow(z)
  round(1 + sum(z * log(z)) / (n * log(k)), 3)
}

lpa_avepp <- function(z, cls) {
  if (is.null(z) || is.null(cls)) return(NA_real_)
  k <- ncol(z)
  vals <- vapply(seq_len(k), function(j) {
    idx <- cls == j
    if (!any(idx)) return(NA_real_)
    mean(z[idx, j])
  }, numeric(1))
  round(mean(vals, na.rm = TRUE), 3)
}

lpa_class_labels <- function(who5, tfw, cls) {
  who5_m <- tapply(who5, cls, mean, na.rm = TRUE)
  tfw_m  <- tapply(tfw, cls, mean, na.rm = TRUE)
  who5_hi <- who5_m > mean(who5, na.rm = TRUE)
  tfw_hi  <- tfw_m  > mean(tfw, na.rm = TRUE)
  labs <- paste0(
    ifelse(who5_hi, "Higher WHO-5", "Lower WHO-5"),
    " / ",
    ifelse(tfw_hi, "higher thriving", "lower thriving")
  )
  names(labs) <- names(who5_m)
  if (any(duplicated(unname(labs)))) {
    ord <- rank(who5_m, ties.method = "first")
    labs <- paste0("Profile ", ord, " (", labs, ")")
    names(labs) <- names(who5_m)
  }
  unname(labs[as.character(cls)])
}

lpa_item_class_labels <- function(who5, tfw, peer, cls) {
  who5_m <- tapply(who5, cls, mean, na.rm = TRUE)
  tfw_m  <- tapply(tfw, cls, mean, na.rm = TRUE)
  peer_m <- tapply(peer, cls, mean, na.rm = TRUE)
  labs <- paste0(
    ifelse(who5_m > mean(who5, na.rm = TRUE), "Higher WHO-5", "Lower WHO-5"),
    " / ",
    ifelse(tfw_m > mean(tfw, na.rm = TRUE), "higher thriving", "lower thriving"),
    " / ",
    ifelse(peer_m > mean(peer, na.rm = TRUE), "higher peer support", "lower peer support")
  )
  names(labs) <- names(who5_m)
  if (any(duplicated(unname(labs)))) {
    ord <- rank(who5_m, ties.method = "first")
    labs <- paste0("Profile ", ord, " (", labs, ")")
    names(labs) <- names(who5_m)
  }
  unname(labs[as.character(cls)])
}

# Gaussian-mixture LPA on a numeric indicator matrix (standardised columns).
# Enumerates k = 1–5 × EEI/VVI/EEE/VVV. Selection matches the Section 6 joint LPA.
fit_lpa_matrix <- function(X, max_k = 5, models = c("EEI", "VVI", "EEE", "VVV")) {
  X <- as.matrix(X)
  storage.mode(X) <- "double"
  ok <- rowSums(is.finite(X)) == ncol(X)
  n <- sum(ok)
  out <- list(
    ok = ok, n = n, enum = tibble(), selected = NULL, fit = NULL,
    class_id = rep(NA_integer_, nrow(X)),
    reason = "Too few complete cases for LPA."
  )
  if (n < 20 || ncol(X) < 2) return(out)

  Xs <- scale(X[ok, , drop = FALSE])
  rows <- list()
  fits <- list()
  for (g in seq_len(max_k)) {
    for (m in models) {
      key <- paste(m, g, sep = "-")
      fit <- tryCatch(
        mclust::Mclust(Xs, G = g, modelNames = m, verbose = FALSE),
        error = function(e) NULL
      )
      if (is.null(fit) || is.null(fit$loglik) || is.null(fit$classification)) next
      ll <- as.numeric(fit$loglik)
      p  <- as.numeric(fit$df)
      z  <- fit$z
      cls <- fit$classification
      tab <- table(factor(cls, levels = seq_len(g)))
      min_n <- as.integer(min(tab))
      min_pct <- round(100 * min_n / n, 1)
      ent <- lpa_entropy(z)
      avepp <- lpa_avepp(z, cls)
      bic_conv <- -2 * ll + p * log(n)
      aic <- -2 * ll + 2 * p
      sabic <- -2 * ll + p * log((n + 2) / 24)
      en <- if (is.null(z) || g < 2) 0 else -sum(pmin(pmax(z, 1e-12), 1) * log(pmin(pmax(z, 1e-12), 1)))
      icl_conv <- bic_conv + 2 * en
      rows[[key]] <- tibble(
        Model = m,
        k = g,
        npar = p,
        loglik = round(ll, 1),
        BIC = round(bic_conv, 1),
        AIC = round(aic, 1),
        SABIC = round(sabic, 1),
        ICL = round(icl_conv, 1),
        mclust_BIC = round(as.numeric(fit$bic), 1),
        entropy = ent,
        AvePP = avepp,
        smallest_n = min_n,
        smallest_pct = min_pct
      )
      fits[[key]] <- fit
    }
  }
  enum <- bind_rows(rows)
  if (nrow(enum) == 0) {
    out$reason <- "No LPA model could be estimated."
    return(out)
  }
  enum <- enum |>
    mutate(
      candidate = k >= 2 & smallest_pct >= 5 & entropy >= 0.60,
      selected = FALSE
    )

  pick_from <- function(dat, why) {
    if (nrow(dat) == 0) return(NULL)
    dat <- dat |> arrange(ICL, BIC, k, Model) |> slice(1)
    list(row = dat, why = why)
  }
  screened <- enum |> filter(candidate)
  hi_ent <- screened |> filter(entropy >= 0.80)
  picked <- pick_from(
    hi_ent,
    "Lowest ICL among k ≥ 2 solutions with smallest class ≥ 5% and entropy ≥ 0.80 (ICL favours separated classes; BIC alone can over-extract slices of a correlated cloud)."
  )
  if (is.null(picked)) {
    picked <- pick_from(
      screened,
      "No solution reached entropy ≥ 0.80; selected lowest ICL among k ≥ 2 with smallest class ≥ 5% and entropy ≥ 0.60."
    )
  }
  if (is.null(picked)) {
    picked <- pick_from(
      enum |> filter(k >= 2, smallest_n >= 10),
      "No solution met the 5% / entropy screens; selected lowest ICL among k ≥ 2 with smallest class n ≥ 10."
    )
  }
  if (is.null(picked)) {
    picked <- pick_from(
      enum |> filter(k >= 2),
      "No screened solution was available; selected lowest ICL among k ≥ 2."
    )
  }
  if (is.null(picked)) {
    picked <- pick_from(enum, "Only a 1-class model could be estimated.")
  }
  pick <- picked$row
  reason <- picked$why

  key <- paste(pick$Model, pick$k, sep = "-")
  fit <- fits[[key]]
  enum$selected[enum$Model == pick$Model & enum$k == pick$k] <- TRUE
  enum$bic_best <- FALSE
  enum$bic_best[which.min(enum$BIC)] <- TRUE

  class_id <- rep(NA_integer_, nrow(X))
  class_id[ok] <- as.integer(fit$classification)
  out$enum <- enum
  out$selected <- pick
  out$fit <- fit
  out$class_id <- class_id
  out$reason <- reason
  out
}

# Joint LPA on WHO-5 + TfWQ (standardised). Enumerates k = 1–5 × EEI/VVI/EEE/VVV.
fit_joint_lpa <- function(who5, tfw, max_k = 5, models = c("EEI", "VVI", "EEE", "VVV")) {
  X <- cbind(who5 = who5, tfw = tfw)
  out <- fit_lpa_matrix(X, max_k = max_k, models = models)
  out$class_lab <- rep(NA_character_, length(who5))
  out$looks_2x2 <- FALSE
  if (is.null(out$fit) || is.null(out$selected)) {
    out$class_lab <- factor(out$class_lab)
    return(out)
  }
  ok <- out$ok
  cls <- out$class_id[ok]
  labs_ok <- lpa_class_labels(who5[ok], tfw[ok], cls)
  who5_m <- tapply(who5[ok], cls, mean, na.rm = TRUE)
  lab_by_id <- tapply(labs_ok, cls, function(v) v[1])
  lab_levels <- unname(lab_by_id[order(who5_m)])
  class_lab <- rep(NA_character_, length(who5))
  class_lab[ok] <- labs_ok
  out$class_lab <- factor(class_lab, levels = lab_levels)
  who5_hi <- tapply(who5[ok], cls, mean, na.rm = TRUE) > mean(who5[ok])
  tfw_hi  <- tapply(tfw[ok], cls, mean, na.rm = TRUE) > mean(tfw[ok])
  out$looks_2x2 <- isTRUE(out$selected$k == 4) && length(unique(paste(who5_hi, tfw_hi))) == 4
  out
}

who5_clinical_cut <- 13L
who5_poor_lab <- "Poor wellbeing (≤13)"
who5_ok_lab   <- "Adequate wellbeing (14–25)"
who5_fill <- setNames(c("#E15759", "#59A14F"), c(who5_poor_lab, who5_ok_lab))
agree_fill <- c(
  "Strongly disagree" = "#E15759",
  "Disagree" = "#F28E2B",
  "Neutral" = "#BAB0AC",
  "Agree" = "#76B7B2",
  "Strongly agree" = "#59A14F"
)
matrix_fill <- c(
  "Poor WHO-5 / Below US average" = "#E15759",
  "Poor WHO-5 / At or above US average" = "#F28E2B",
  "Adequate WHO-5 / Below US average" = "#4E79A7",
  "Adequate WHO-5 / At or above US average" = "#59A14F"
)
tfw_below_lab <- "Below US average (T < 50)"
tfw_avg_lab   <- "At or above US average (T ≥ 50)"
tfw_t_cut <- 50

# Official short-form T-score lookup (Gundersen et al. 2025 Scoring Guide, Appendix A).
# Raw summed score on 1–6 items (range 8–48) → T-score (US validation mean 50, SD 10).
tfw_t_lookup <- tibble(
  tfw_6 = 8:48,
  tfw_t = c(
    12.9, 15.8, 18.1, 20.0, 21.7, 23.2, 24.7, 26.1, 27.4, 28.7,
    29.9, 31.1, 32.3, 33.5, 34.6, 35.7, 36.9, 38.0, 39.1, 40.2,
    41.2, 42.3, 43.4, 44.5, 45.7, 46.8, 47.9, 49.0, 50.2, 51.4,
    52.6, 53.9, 55.2, 56.5, 58.0, 59.5, 61.1, 63.0, 65.1, 67.7,
    71.6
  ),
  tfw_t_sem = c(
    4.458, 4.011, 3.799, 3.658, 3.552, 3.473, 3.415, 3.372, 3.340, 3.317,
    3.301, 3.290, 3.284, 3.281, 3.282, 3.284, 3.288, 3.293, 3.299, 3.305,
    3.311, 3.318, 3.325, 3.333, 3.341, 3.350, 3.358, 3.368, 3.379, 3.393,
    3.412, 3.436, 3.469, 3.514, 3.574, 3.655, 3.759, 3.903, 4.102, 4.425,
    5.242
  )
)

# Linear map of a 1–5 item sum (8–40) onto the official 1–6 sum (8–48).
scale_tfw_sum_to_6 <- function(s5) {
  8 + (as.numeric(s5) - 8) * (40 / 32)
}
lpa_palette <- c("#E15759", "#4E79A7", "#59A14F", "#F28E2B", "#B07AA1")

tfw_focus_items <- c(4, 5, 6, 9, 10)
tfw_item_lab <- c(
  "4"  = "Item 4 — Treated fairly at work",
  "5"  = "Item 5 — Healthy work–life balance",
  "6"  = "Item 6 — Paid fairly",
  "9"  = "Item 9 — Psychologically safe at work",
  "10" = "Item 10 — Can voice concerns without trouble"
)
lpa_all_item_lab <- c(
  p1_1  = "WHO-5 1 — Cheerful and in good spirits",
  p1_2  = "WHO-5 2 — Calm and relaxed",
  p1_3  = "WHO-5 3 — Active and vigorous",
  p1_4  = "WHO-5 4 — Fresh and rested",
  p1_5  = "WHO-5 5 — Daily life interesting",
  p2_1  = "Peer 1 — Support from colleagues",
  p2_2  = "Peer 2 — Can talk to colleagues",
  p2_3  = "TfWQ 3 — Love my job",
  p2_4  = "TfWQ 4 — Treated fairly at work",
  p2_5  = "TfWQ 5 — Healthy work–life balance",
  p2_6  = "TfWQ 6 — Paid fairly",
  p2_7  = "TfWQ 7 — Input into work decisions",
  p2_8  = "TfWQ 8 — Manage job demands",
  p2_9  = "TfWQ 9 — Psychologically safe at work",
  p2_10 = "TfWQ 10 — Can voice concerns without trouble"
)

find_hk_forms_xlsx <- function() {
  pattern <- "1-107.*\\.xlsx$"
  dirs <- unique(c(
    getwd(),
    "C:/Users/chankalong/OneDrive - Baptist Oi Kwan Social Service/KaLong/non_refresh/kt-eap/analysis",
    "C:/Users/chankalong/Downloads"
  ))
  hits <- unlist(lapply(dirs, function(d) {
    if (!dir.exists(d)) return(character())
    list.files(d, pattern = pattern, full.names = TRUE)
  }), use.names = FALSE)
  hits <- hits[!grepl("emotion_twister_tables", basename(hits))]
  if (length(hits) == 0) return(NA_character_)
  hits[[1]]
}

map_hk_forms_xlsx <- function(path) {
  xl <- readxl::read_xlsx(path)
  pick <- function(pattern) {
    hit <- names(xl)[stringr::str_detect(names(xl), pattern)]
    if (length(hit) == 0) stop("No column matches: ", pattern)
    xl[[hit[[1]]]]
  }
  num <- function(x) as.integer(as.character(x))
  who <- cbind(
    num(pick("^我感覺快樂")),
    num(pick("^我感到平靜")),
    num(pick("^我感到充滿活力")),
    num(pick("^我睡醒時")),
    num(pick("^我的日常生活"))
  )
  peer <- cbind(
    num(pick("^我願意與他人分享")),
    num(pick("^我願意向情緒"))
  )
  tfw <- cbind(
    num(pick("^我喜歡我的工作")),
    num(pick("^在工作中，我受到公平對待")),
    num(pick("^我能在工作與工作以外")),
    num(pick("^我從工作獲得公平的報酬")),
    num(pick("^對於影響我工作的決策")),
    num(pick("^我能輕鬆應付工作")),
    num(pick("^在工作中，我感到具有心理安全感")),
    num(pick("^在工作中，我可以提出關注"))
  )
  attn <- num(pick("^為確保你有認真閱讀"))
  age_raw <- as.character(pick("^年齡組別"))
  age_raw <- stringr::str_replace_all(age_raw, "\u2013", "-")
  age_raw <- stringr::str_replace_all(age_raw, "歲或以上", "+")
  age_raw <- stringr::str_trim(stringr::str_remove_all(age_raw, "歲"))
  gender_raw <- as.character(pick("^性別$"))
  edu_raw <- as.character(pick("^教育程度$"))
  job_raw <- as.character(pick("^職級$"))
  job_other_raw <- stringr::str_trim(as.character(pick("請註明職級")))
  ans <- function(v) ifelse(is.na(v), NA_character_, as.character(v))
  tibble(
    id = paste0("hk-forms-", pick("^ID$")),
    submittedAt = format(as.POSIXct(pick("^(完成時間|Completion time)$"), tz = "UTC"), "%Y-%m-%dT%H:%M:%SZ"),
    locationCode = "HK-forms",
    data_source = "HK Forms",
    attn_check = attn,
    `demographics.resultEmail` = NA_character_,
    `demographics.age` = age_raw,
    `demographics.gender` = dplyr::case_when(
      gender_raw %in% c("女", "女性") ~ "female",
      gender_raw %in% c("男", "男性") ~ "male",
      gender_raw %in% c("其他") ~ "other",
      TRUE ~ NA_character_
    ),
    `demographics.occupation` = dplyr::case_when(
      stringr::str_detect(job_raw, "前線|一般") ~ "frontline",
      stringr::str_detect(job_raw, "中層") ~ "mid-level",
      stringr::str_detect(job_raw, "高層") ~ "senior-level",
      stringr::str_detect(tolower(job_other_raw), "director") ~ "senior-level",
      job_other_raw %in% c("老闆", "老板") ~ "senior-level",
      job_raw %in% c("其他") ~ "other",
      TRUE ~ NA_character_
    ),
    `demographics.education` = dplyr::case_when(
      edu_raw %in% c("小學") ~ "primary",
      edu_raw %in% c("初中") ~ "junior-secondary",
      edu_raw %in% c("高中") ~ "senior-secondary",
      edu_raw %in% c("專上") ~ "tertiary",
      edu_raw %in% c("學士") ~ "bachelor",
      edu_raw %in% c("碩士") ~ "master",
      edu_raw %in% c("博士") ~ "phd",
      edu_raw %in% c("其他") ~ "other",
      TRUE ~ NA_character_
    ),
    `demographics.workStatus` = dplyr::case_when(
      pick("^就業狀況$") %in% c("全職") ~ "full-time",
      pick("^就業狀況$") %in% c("兼職") ~ "part-time",
      pick("^就業狀況$") %in% c("沒有工作") ~ "no-work",
      pick("^就業狀況$") %in% c("其他") ~ "other",
      TRUE ~ NA_character_
    ),
    part1ScoreSum = rowSums(who),
    part2PeerSupportSum = rowSums(peer),
    part2ThrivingSfSum = rowSums(tfw),
    `answers.part1-1` = ans(who[, 1]),
    `answers.part1-2` = ans(who[, 2]),
    `answers.part1-3` = ans(who[, 3]),
    `answers.part1-4` = ans(who[, 4]),
    `answers.part1-5` = ans(who[, 5]),
    `answers.part2-1` = ans(peer[, 1]),
    `answers.part2-2` = ans(peer[, 2]),
    `answers.part2-3` = ans(tfw[, 1]),
    `answers.part2-4` = ans(tfw[, 2]),
    `answers.part2-5` = ans(tfw[, 3]),
    `answers.part2-6` = ans(tfw[, 4]),
    `answers.part2-7` = ans(tfw[, 5]),
    `answers.part2-8` = ans(tfw[, 6]),
    `answers.part2-9` = ans(tfw[, 7]),
    `answers.part2-10` = ans(tfw[, 8])
  )
}
```

```{r}
#| label: load-data

api_cache <- Sys.getenv("KT_API_CACHE", unset = "")
api_key <- Sys.getenv("SURVEY_API_KEY", unset = "")
if (nzchar(api_cache) && file.exists(api_cache)) {
  data_raw <- paste(readLines(api_cache, warn = FALSE, encoding = "UTF-8"), collapse = "\n")
} else {
  if (!nzchar(api_key)) {
    stop(
      "SURVEY_API_KEY is not set. Add it to .Renviron for local renders, or as a Connect Cloud secret.",
      call. = FALSE
    )
  }
  resp <- request("https://emotion-twister-survey.vercel.app/api/admin/export-data") |>
    req_headers(`x-api-key` = api_key) |>
    req_perform()
  data_raw <- resp |> resp_body_string()
  if (nzchar(api_cache)) {
    writeLines(data_raw, api_cache, useBytes = TRUE)
  }
}
data_json <- fromJSON(data_raw, flatten = TRUE)
submissions_all <- as_tibble(data_json$submissions) |>
  mutate(
    data_source = "API",
    attn_check = NA_integer_
  )

n_hk_forms_raw <- 0
hk_forms <- tibble()
if (isTRUE(include_hk_forms)) {
  hk_xlsx_path <- find_hk_forms_xlsx()
  hk_forms <- if (!is.na(hk_xlsx_path)) map_hk_forms_xlsx(hk_xlsx_path) else tibble()
  n_hk_forms_raw <- nrow(hk_forms)
}
submissions_all <- submissions_all |>
  mutate(
    id = as.character(id),
    locationCode = as.character(locationCode),
    submittedAt = as.character(submittedAt)
  )
if (n_hk_forms_raw > 0) {
  hk_forms <- hk_forms |>
    mutate(
      id = as.character(id),
      locationCode = as.character(locationCode),
      submittedAt = as.character(submittedAt)
    )
  submissions_all <- bind_rows(submissions_all, hk_forms)
}
```

```{r}
#| label: filter-and-clean

df_all <- submissions_all |>
  mutate(
    submittedAt = as_datetime(submittedAt),
    submit_date = as_date(submittedAt),
    email       = demographics.resultEmail
  )

in_include_windows <- function(dates, locs, windows) {
  if (length(windows) == 0) return(rep(TRUE, length(dates)))
  Reduce("|", lapply(windows, function(w) {
    ok <- dates >= as.Date(w$start) & dates <= as.Date(w$end)
    if (!is.null(w$locations) && length(w$locations) > 0) {
      ok <- ok & as.character(locs) %in% as.character(w$locations)
    }
    ok
  }))
}

if (!isTRUE(use_all_dates)) {
  if (length(include_windows) > 0) {
    df_all <- df_all |>
      filter(in_include_windows(submit_date, locationCode, include_windows))
  } else {
    df_all <- df_all |>
      filter(submit_date >= start_date, submit_date <= end_date)
  }
}

df_all <- df_all |> arrange(submittedAt)

is_in_excluded_period <- function(dates, periods) {
  if (length(periods) == 0) return(rep(FALSE, length(dates)))
  Reduce("|", lapply(periods, function(p) dates >= p$start & dates <= p$end))
}

n_all <- nrow(df_all)

df_all <- df_all |>
  mutate(
    is_bokss         = grepl("@bokss.org.hk", email, ignore.case = TRUE),
    is_dup_email     = !is.na(email) & email != "" & duplicated(email),
    is_excl_period   = is_in_excluded_period(submit_date, exclude_periods),
    is_job_other     = !is.na(demographics.occupation) & demographics.occupation == "other",
    is_gender_other  = !is.na(demographics.gender) & demographics.gender == "other",
    is_edu_other     = !is.na(demographics.education) & demographics.education == "other",
    is_attn_fail     = !is.na(attn_check) & attn_check != 3L,
    is_valid         = !is_bokss & !is_dup_email & !is_excl_period & !is_attn_fail &
      !is_job_other & !is_gender_other & !is_edu_other
  )

n_bokss        <- sum(df_all$is_bokss)
n_dup          <- sum(df_all$is_dup_email & !df_all$is_bokss)
n_excl_period  <- sum(df_all$is_excl_period & !df_all$is_bokss & !df_all$is_dup_email)
n_attn_fail    <- sum(df_all$is_attn_fail & !df_all$is_bokss & !df_all$is_dup_email & !df_all$is_excl_period)
n_job_other    <- sum(df_all$is_job_other & !df_all$is_bokss & !df_all$is_dup_email &
                        !df_all$is_excl_period & !df_all$is_attn_fail)
n_gender_other <- sum(df_all$is_gender_other & !df_all$is_bokss & !df_all$is_dup_email &
                        !df_all$is_excl_period & !df_all$is_attn_fail & !df_all$is_job_other)
n_edu_other    <- sum(df_all$is_edu_other & !df_all$is_bokss & !df_all$is_dup_email &
                        !df_all$is_excl_period & !df_all$is_attn_fail &
                        !df_all$is_job_other & !df_all$is_gender_other)

df <- df_all |>
  filter(is_valid) |>
  mutate(
    age        = factor(demographics.age,
                        levels = c("18-24", "25-29", "30-39", "40-49", "50-59", "60+")),
    gender     = factor(demographics.gender,
                        levels = c("female", "male"),
                        labels = c("Female", "Male")),
    job_grade  = factor(demographics.occupation,
                        levels = c("frontline", "mid-level", "senior-level"),
                        labels = c("一般職員", "Mid-level", "Senior-level")),
    education  = factor(demographics.education,
                        levels = c("primary", "junior-secondary", "senior-secondary",
                                   "tertiary", "bachelor", "master", "phd"),
                        labels = c("Primary", "Junior Secondary", "Senior Secondary",
                                   "Tertiary", "Bachelor", "Master", "PhD")),
    who5 = part1ScoreSum,
    tfw  = part2ThrivingSfSum,
    peer = part2PeerSupportSum,
    wellbeing_cat = if_else(
      who5 <= who5_clinical_cut,
      who5_poor_lab,
      who5_ok_lab
    ) |> factor(levels = c(who5_poor_lab, who5_ok_lab)),
    tfw_6 = as.integer(pmin(48, pmax(8, round(scale_tfw_sum_to_6(tfw)))))
  ) |>
  left_join(tfw_t_lookup, by = "tfw_6") |>
  mutate(
    tfw_t_cat = if_else(
      tfw_t < tfw_t_cut,
      tfw_below_lab,
      tfw_avg_lab
    ) |> factor(levels = c(tfw_below_lab, tfw_avg_lab)),
    age = droplevels(age),
    gender = droplevels(gender),
    job_grade = droplevels(job_grade),
    education = droplevels(education)
  )

n_total   <- nrow(df)
n_valid_api   <- sum(df$data_source == "API", na.rm = TRUE)
n_valid_excel <- sum(df$data_source == "HK Forms", na.rm = TRUE)
pct_valid <- if (n_all > 0) round(n_total / n_all * 100, 1) else 0
date_min  <- if (n_total > 0) min(df$submit_date) else start_date
date_max  <- if (n_total > 0) max(df$submit_date) else end_date
if (isTRUE(use_all_dates) && n_total > 0) {
  start_date <- date_min
  end_date   <- date_max
}

# Item-level TfWQ scores for focus items
item_long <- df |>
  select(id, age, job_grade, starts_with("answers.part2-")) |>
  pivot_longer(
    cols = starts_with("answers.part2-"),
    names_to = "item_raw",
    values_to = "answer"
  ) |>
  mutate(
    item_n = as.integer(str_extract(item_raw, "\\d+$")),
    score  = as.integer(str_extract(answer, "^\\d+")),
    response = factor(
      score,
      levels = 1:5,
      labels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")
    )
  ) |>
  filter(item_n %in% tfw_focus_items) |>
  mutate(
    item = factor(as.character(item_n), levels = as.character(tfw_focus_items),
                  labels = unname(tfw_item_lab[as.character(tfw_focus_items)])),
    agree = score >= 4
  )
```

The dataset contains **`{r} n_all`** submissions in the selected period. After exclusions, **`{r} n_total`** valid responses (`{r} pct_valid`%) collected between `{r} format(date_min, "%d %B %Y")` and `{r} format(date_max, "%d %B %Y")` are analysed.

# Data overview

```{r}
#| label: overview-table

overview_tbl <- tibble(
  Metric = c(
    "Organisation",
    "Configured date range",
    "Total submissions (in window)",
    "From live survey API",
    "From HK Forms Excel (raw)",
    "Excluded — @bokss.org.hk emails",
    "Excluded — duplicate emails (kept first)",
    "Excluded — invalid periods",
    "Excluded — attention check (Forms)",
    "Excluded — job grade Other",
    "Excluded — gender Other",
    "Excluded — education Other",
    "Valid submissions",
    "Valid from live survey API",
    "Valid from HK Forms Excel",
    "Valid submission rate",
    "Observed date range",
    "Location code(s)"
  ),
  Value = c(
    company_name,
    if (isTRUE(use_all_dates)) {
      "All available periods"
    } else {
      period_cover_lab
    },
    as.character(n_all),
    as.character(sum(df_all$data_source == "API", na.rm = TRUE)),
    as.character(n_hk_forms_raw),
    as.character(n_bokss),
    as.character(n_dup),
    as.character(n_excl_period),
    as.character(n_attn_fail),
    as.character(n_job_other),
    as.character(n_gender_other),
    as.character(n_edu_other),
    as.character(n_total),
    as.character(n_valid_api),
    as.character(n_valid_excel),
    paste0(pct_valid, "%"),
    paste(format(date_min, "%d %b %Y"), "–", format(date_max, "%d %b %Y")),
    if (n_total > 0) paste(unique(df$locationCode), collapse = ", ") else "—"
  )
)

show_tbl(overview_tbl, "00_overview", "Sample overview")
```

```{r}
#| label: submissions-over-time
#| fig-cap: "Daily valid survey submissions."

if (n_total > 0) {
  df |>
    count(submit_date) |>
    ggplot(aes(x = submit_date, y = n)) +
    geom_col(fill = "#4E79A7", width = 0.8) +
    labs(title = "Daily survey submissions", x = "Date", y = "Number of submissions",
         caption = src_cap()) +
    theme_report() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}
```

# 1. Demographic description

```{r}
#| label: demo-table

demo_one <- function(var, label) {
  df |>
    filter(!is.na(.data[[var]])) |>
    count(.data[[var]], name = "n") |>
    mutate(
      Characteristic = label,
      Level = as.character(.data[[var]]),
      pct = round(100 * n / sum(n), 1)
    ) |>
    select(Characteristic, Level, n, pct)
}

demo_tbl <- bind_rows(
  demo_one("age", "Age group"),
  demo_one("gender", "Gender"),
  demo_one("job_grade", "Job grade"),
  demo_one("education", "Education")
)

show_tbl(demo_tbl, "01_demographics", "Demographic description (n and %)")
```

```{r}
#| label: demo-plots
#| fig-height: 8
#| fig-cap: "Demographic counts and percentages."

plot_demo <- function(var, title, xlab) {
  df |>
    filter(!is.na(.data[[var]])) |>
    count(.data[[var]], name = "n") |>
    mutate(pct = n / sum(n), grp = .data[[var]]) |>
    ggplot(aes(x = grp, y = n, fill = grp)) +
    geom_col(show.legend = FALSE) +
    geom_text(aes(label = paste0(n, " (", percent(pct, accuracy = 0.1), ")")),
              vjust = -0.35, size = 3) +
    labs(title = title, x = xlab, y = "Count", caption = src_cap()) +
    theme_report() +
    scale_y_continuous(expand = expansion(mult = c(0, 0.18)))
}

if (n_total > 0) {
  p_age <- plot_demo("age", "Age group", "Age group") + scale_fill_brewer(palette = "Blues")
  p_sex <- plot_demo("gender", "Gender", "Gender") +
    scale_fill_manual(values = c("Female" = "#F28E2B", "Male" = "#4E79A7", "Other" = "#BAB0AC"))
  p_job <- df |>
    filter(!is.na(job_grade)) |>
    count(job_grade, name = "n") |>
    mutate(pct = n / sum(n), job_grade = fct_rev(job_grade)) |>
    ggplot(aes(x = job_grade, y = n, fill = job_grade)) +
    geom_col(show.legend = FALSE) +
    geom_text(aes(label = paste0(n, " (", percent(pct, accuracy = 0.1), ")")),
              hjust = -0.1, size = 3) +
    coord_flip() +
    scale_fill_brewer(palette = "Set2") +
    labs(title = "Job grade", x = NULL, y = "Count", caption = src_cap()) +
    theme_report() +
    scale_y_continuous(expand = expansion(mult = c(0, 0.22)))
  p_edu <- df |>
    filter(!is.na(education)) |>
    count(education, name = "n") |>
    mutate(pct = n / sum(n), education = fct_rev(education)) |>
    ggplot(aes(x = education, y = n, fill = education)) +
    geom_col(show.legend = FALSE) +
    geom_text(aes(label = paste0(n, " (", percent(pct, accuracy = 0.1), ")")),
              hjust = -0.1, size = 3) +
    coord_flip() +
    scale_fill_brewer(palette = "Pastel1") +
    labs(title = "Education", x = NULL, y = "Count", caption = src_cap()) +
    theme_report() +
    scale_y_continuous(expand = expansion(mult = c(0, 0.22)))

  print(p_age)
  print(p_sex)
  print(p_job)
  print(p_edu)
}
```

# 2. WHO-5 average score

WHO-5 total scores range from **0 to 25**.

```{r}
#| label: who5-overall-stats

who5_overall <- tibble(
  Scale = "WHO-5",
  n = n_total,
  mean = round(mean(df$who5, na.rm = TRUE), 2),
  sd = round(sd(df$who5, na.rm = TRUE), 2),
  median = round(median(df$who5, na.rm = TRUE), 2),
  min = min(df$who5, na.rm = TRUE),
  max = max(df$who5, na.rm = TRUE)
)

show_tbl(who5_overall, "02_who5_total_average", "WHO-5 total average")
```

The mean WHO-5 score is **`{r} who5_overall$mean`** (SD = `{r} who5_overall$sd`; median = `{r} who5_overall$median`; n = `{r} who5_overall$n`).

```{r}
#| label: who5-distribution
#| fig-cap: "Distribution of WHO-5 total scores with the clinical screening cutoff (≤13)."

if (n_total > 0) {
  ggplot(df, aes(x = who5)) +
    geom_histogram(binwidth = 1, fill = "#4E79A7", colour = "white") +
    geom_vline(xintercept = who5_clinical_cut + 0.5, colour = "#E15759",
               linetype = "dashed", linewidth = 1) +
    labs(title = "WHO-5 total score distribution",
         x = "WHO-5 score (0–25)", y = "Count",
         caption = paste0(src_cap(), " · Dashed line: clinical cutoff (≤13)")) +
    theme_report()
}
```

## Compare by age group

```{r}
#| label: who5-by-age-table

who5_age <- mean_by_group(df, age, who5) |>
  rename(`Age group` = age)

show_tbl(who5_age, "02_who5_mean_by_age", "WHO-5 mean by age group")
```

```{r}
#| label: who5-by-age-plot
#| fig-cap: "Mean WHO-5 score by age group, with standard error bars."

if (nrow(who5_age) > 0) {
  ggplot(who5_age, aes(x = `Age group`, y = mean, fill = `Age group`)) +
    geom_col(show.legend = FALSE) +
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.25, na.rm = TRUE) +
    geom_text(aes(label = sprintf("%.1f\nn=%s", mean, n)), vjust = -0.4, size = 3) +
    scale_fill_brewer(palette = "Blues") +
    coord_cartesian(ylim = c(0, 26)) +
    labs(title = "Mean WHO-5 score by age group",
         x = "Age group", y = "Mean WHO-5 (± SE)", caption = src_cap()) +
    theme_report()
}
```

## Compare by job grade

```{r}
#| label: who5-by-job-table

who5_job <- mean_by_group(df, job_grade, who5) |>
  rename(`Job grade` = job_grade)

show_tbl(who5_job, "02_who5_mean_by_job", "WHO-5 mean by job grade")
```

```{r}
#| label: who5-by-job-plot
#| fig-cap: "Mean WHO-5 score by job grade, with standard error bars."

if (nrow(who5_job) > 0) {
  ggplot(who5_job, aes(x = fct_rev(`Job grade`), y = mean, fill = `Job grade`)) +
    geom_col(show.legend = FALSE) +
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.25, na.rm = TRUE) +
    geom_text(aes(label = sprintf("%.1f (n=%s)", mean, n)), hjust = -0.1, size = 3) +
    coord_flip() +
    scale_fill_brewer(palette = "Set2") +
    labs(title = "Mean WHO-5 score by job grade",
         x = NULL, y = "Mean WHO-5 (± SE)", caption = src_cap()) +
    theme_report() +
    scale_y_continuous(expand = expansion(mult = c(0, 0.18)), limits = c(0, 26))
}
```

# 3. WHO-5 category

Categories follow the **WHO-5 clinical screening cutoff**: **Poor wellbeing (raw score ≤13)** versus **Adequate wellbeing (14–25)**. A score of 13 or below is the recommended threshold for further assessment.

## Total percentage

```{r}
#| label: who5-cat-total-table

who5_cat_total <- df |>
  count(wellbeing_cat, name = "n") |>
  mutate(pct = round(100 * n / sum(n), 1)) |>
  rename(Category = wellbeing_cat)

show_tbl(who5_cat_total, "03_who5_category_total", "WHO-5 category — overall")
```

```{r}
#| label: who5-cat-total-plot
#| fig-cap: "Overall WHO-5 category distribution."

if (nrow(who5_cat_total) > 0) {
  ggplot(who5_cat_total, aes(x = Category, y = n, fill = Category)) +
    geom_col(show.legend = FALSE) +
    geom_text(aes(label = paste0(n, "\n(", pct, "%)")), vjust = -0.2, size = 3.5) +
    scale_fill_manual(values = who5_fill) +
    labs(title = "WHO-5 category distribution",
         x = "Category", y = "Count", caption = src_cap()) +
    theme_report() +
    scale_y_continuous(expand = expansion(mult = c(0, 0.2)))
}
```

## Compare by age group

```{r}
#| label: who5-cat-age-table

who5_cat_age <- cat_by_group(df, age, wellbeing_cat) |>
  rename(`Age group` = age, Category = wellbeing_cat)

show_tbl(who5_cat_age, "03_who5_category_by_age", "WHO-5 category by age group")
```

```{r}
#| label: who5-cat-age-plot
#| fig-cap: "WHO-5 category mix within each age group."

if (nrow(who5_cat_age) > 0) {
  ggplot(who5_cat_age, aes(x = `Age group`, y = n / group_n, fill = Category)) +
    geom_col(position = "stack") +
    geom_text(aes(label = ifelse(pct >= 8, paste0(pct, "%"), "")),
              position = position_stack(vjust = 0.5), size = 3, colour = "white") +
    scale_y_continuous(labels = percent_format()) +
    scale_fill_manual(values = who5_fill) +
    labs(title = "WHO-5 category by age group",
         x = "Age group", y = "Percentage within age group",
         fill = "Category", caption = src_cap()) +
    theme_report()
}
```

## Compare by job grade

```{r}
#| label: who5-cat-job-table

who5_cat_job <- cat_by_group(df, job_grade, wellbeing_cat) |>
  rename(`Job grade` = job_grade, Category = wellbeing_cat)

show_tbl(who5_cat_job, "03_who5_category_by_job", "WHO-5 category by job grade")
```

```{r}
#| label: who5-cat-job-plot
#| fig-cap: "WHO-5 category mix within each job grade."

if (nrow(who5_cat_job) > 0) {
  ggplot(who5_cat_job, aes(x = fct_rev(`Job grade`), y = n / group_n, fill = Category)) +
    geom_col(position = "stack") +
    geom_text(aes(label = ifelse(pct >= 8, paste0(pct, "%"), "")),
              position = position_stack(vjust = 0.5), size = 3, colour = "white") +
    coord_flip() +
    scale_y_continuous(labels = percent_format()) +
    scale_fill_manual(values = who5_fill) +
    labs(title = "WHO-5 category by job grade",
         x = NULL, y = "Percentage within job grade",
         fill = "Category", caption = src_cap()) +
    theme_report()
}
```

# 4. Thriving from Work (items 3–10) average

Harvard TfWQ short form = Part 2 items **3–10**. Survey responses are 1–5 (total **8–40**). For comparison with the US validation sample, that sum is linearly rescaled to the official 1–6 metric (**8–48**) and looked up in Harvard’s short-form **T-score** table (mean 50, SD 10). T = 50 is the US-sample average; T = 60 is about one SD higher. Item-level charts below stay on the original 1–5 scale.

```{r}
#| label: tfw-overall-stats

tfw_overall <- tibble(
  Metric = c(
    "Survey sum (1–5 items, 8–40)",
    "Rescaled official sum (1–6 items, 8–48)",
    "US T-score (mean 50, SD 10)"
  ),
  n = n_total,
  mean = c(
    round(mean(df$tfw, na.rm = TRUE), 2),
    round(mean(df$tfw_6, na.rm = TRUE), 2),
    round(mean(df$tfw_t, na.rm = TRUE), 2)
  ),
  sd = c(
    round(sd(df$tfw, na.rm = TRUE), 2),
    round(sd(df$tfw_6, na.rm = TRUE), 2),
    round(sd(df$tfw_t, na.rm = TRUE), 2)
  ),
  median = c(
    round(median(df$tfw, na.rm = TRUE), 2),
    round(median(df$tfw_6, na.rm = TRUE), 2),
    round(median(df$tfw_t, na.rm = TRUE), 2)
  ),
  min = c(min(df$tfw, na.rm = TRUE), min(df$tfw_6, na.rm = TRUE), min(df$tfw_t, na.rm = TRUE)),
  max = c(max(df$tfw, na.rm = TRUE), max(df$tfw_6, na.rm = TRUE), max(df$tfw_t, na.rm = TRUE))
)

tfw_t_cat_tbl <- df |>
  filter(!is.na(tfw_t_cat)) |>
  count(tfw_t_cat, name = "n") |>
  mutate(pct = round(100 * n / sum(n), 1)) |>
  rename(Category = tfw_t_cat)

htmltools::tagList(
  show_tbl(tfw_overall, "04_tfw_total_average", "Thriving from Work — survey sum, rescaled sum, and US T-score"),
  show_tbl(tfw_t_cat_tbl, "04_tfw_t_category", "Thriving T-score vs US average (T = 50)")
)
```

The mean US T-score is **`{r} tfw_overall$mean[3]`** (SD = `{r} tfw_overall$sd[3]`; n = `{r} n_total`). T = 50 is the average in Harvard’s US validation sample.

```{r}
#| label: tfw-distribution
#| fig-cap: "Distribution of US-normed TfWQ T-scores. Dashed line is the US average (T = 50)."

if (n_total > 0) {
  ggplot(df, aes(x = tfw_t)) +
    geom_histogram(binwidth = 2, fill = "#59A14F", colour = "white") +
    geom_vline(xintercept = tfw_t_cut, colour = "#E15759",
               linetype = "dashed", linewidth = 1) +
    labs(title = "Thriving from Work T-score distribution",
         x = "US T-score (50 = validation-sample average)", y = "Count",
         caption = paste0(src_cap(), " · Dashed line: US average (T = 50)")) +
    theme_report()
}
```

## Compare by age group

```{r}
#| label: tfw-by-age-table

tfw_age <- mean_by_group(df, age, tfw_t) |>
  rename(`Age group` = age)

show_tbl(tfw_age, "04_tfw_mean_by_age", "Thriving from Work US T-score mean by age group")
```

```{r}
#| label: tfw-by-age-plot
#| fig-cap: "Mean Thriving from Work US T-score by age group. Dashed line is the US average (T = 50)."

if (nrow(tfw_age) > 0) {
  ggplot(tfw_age, aes(x = `Age group`, y = mean, fill = `Age group`)) +
    geom_col(show.legend = FALSE) +
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.25, na.rm = TRUE) +
    geom_hline(yintercept = tfw_t_cut, linetype = "dashed", colour = "grey30") +
    geom_text(aes(label = sprintf("%.1f\nn=%s", mean, n)), vjust = -0.4, size = 3) +
    scale_fill_brewer(palette = "Greens") +
    coord_cartesian(ylim = c(0, 80)) +
    labs(title = "Mean Thriving from Work T-score by age group",
         x = "Age group", y = "Mean US T-score (± SE)", caption = src_cap()) +
    theme_report()
}
```

## Compare by job grade

```{r}
#| label: tfw-by-job-table

tfw_job <- mean_by_group(df, job_grade, tfw_t) |>
  rename(`Job grade` = job_grade)

show_tbl(tfw_job, "04_tfw_mean_by_job", "Thriving from Work US T-score mean by job grade")
```

```{r}
#| label: tfw-by-job-plot
#| fig-cap: "Mean Thriving from Work US T-score by job grade. Dashed line is the US average (T = 50)."

if (nrow(tfw_job) > 0) {
  ggplot(tfw_job, aes(x = fct_rev(`Job grade`), y = mean, fill = `Job grade`)) +
    geom_col(show.legend = FALSE) +
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.25, na.rm = TRUE) +
    geom_hline(yintercept = tfw_t_cut, linetype = "dashed", colour = "grey30") +
    geom_text(aes(label = sprintf("%.1f (n=%s)", mean, n)), hjust = -0.1, size = 3) +
    coord_flip() +
    scale_fill_brewer(palette = "Set2") +
    labs(title = "Mean Thriving from Work T-score by job grade",
         x = NULL, y = "Mean US T-score (± SE)", caption = src_cap()) +
    theme_report() +
    scale_y_continuous(expand = expansion(mult = c(0, 0.18)), limits = c(0, 80))
}
```

# 5. Thriving from Work items 4, 5, 6, 9, 10

Item-level percentages use the 5-point agreement scale. **Agree %** = Agree + Strongly agree (scores 4–5). English labels follow the Harvard TfWQ short-form sequence mapped to Part 2 items 3–10.

## Total item-level percentage

```{r}
#| label: tfw-item-total-table

item_dist <- item_long |>
  filter(!is.na(response)) |>
  count(item, response, name = "n") |>
  group_by(item) |>
  mutate(item_n = sum(n), pct = round(100 * n / item_n, 1)) |>
  ungroup()

item_agree <- item_long |>
  filter(!is.na(score)) |>
  group_by(item) |>
  summarise(
    n = n(),
    mean = round(mean(score), 2),
    agree_n = sum(agree, na.rm = TRUE),
    agree_pct = round(100 * mean(agree, na.rm = TRUE), 1),
    .groups = "drop"
  )

htmltools::tagList(
  show_tbl(item_agree, "05_tfw_item_agree_total", "Item-level mean and % agree (scores 4–5)"),
  show_tbl(item_dist, "05_tfw_item_distribution_total", "Item-level response percentages")
)
```

```{r}
#| label: tfw-item-total-plot
#| fig-height: 6
#| fig-cap: "Response mix for TfWQ items 4, 5, 6, 9 and 10."

if (nrow(item_dist) > 0) {
  ggplot(item_dist, aes(x = fct_rev(item), y = n / item_n, fill = response)) +
    geom_col(position = "stack") +
    geom_text(aes(label = ifelse(pct >= 8, paste0(pct, "%"), "")),
              position = position_stack(vjust = 0.5), size = 3, colour = "white") +
    coord_flip() +
    scale_y_continuous(labels = percent_format()) +
    scale_fill_manual(values = agree_fill) +
    labs(title = "TfWQ item-level response percentages",
         x = NULL, y = "Percentage", fill = "Response", caption = src_cap()) +
    theme_report()
}
```

```{r}
#| label: tfw-item-agree-plot
#| fig-cap: "Percentage agreeing (score 4–5) on each focus item."

if (nrow(item_agree) > 0) {
  ggplot(item_agree, aes(x = fct_rev(item), y = agree_pct / 100, fill = item)) +
    geom_col(show.legend = FALSE) +
    geom_text(aes(label = paste0(agree_pct, "%")), hjust = -0.1, size = 3.2) +
    coord_flip() +
    scale_y_continuous(labels = percent_format(), limits = c(0, 1.08)) +
    scale_fill_brewer(palette = "Greens") +
    labs(title = "% agree (4–5) by TfWQ item",
         x = NULL, y = "Percentage agreeing", caption = src_cap()) +
    theme_report()
}
```

## Item-level percentage by age group

```{r}
#| label: tfw-item-age-table

item_age_dist <- item_long |>
  filter(!is.na(age), !is.na(response)) |>
  count(age, item, response, name = "n") |>
  group_by(age, item) |>
  mutate(group_n = sum(n), pct = round(100 * n / group_n, 1)) |>
  ungroup() |>
  rename(`Age group` = age)

item_age_agree <- item_long |>
  filter(!is.na(age), !is.na(score)) |>
  group_by(age, item) |>
  summarise(
    n = n(),
    agree_pct = round(100 * mean(agree, na.rm = TRUE), 1),
    .groups = "drop"
  ) |>
  rename(`Age group` = age)

htmltools::tagList(
  show_tbl(item_age_agree, "05_tfw_item_agree_by_age", "% agree by item and age group"),
  show_tbl(item_age_dist, "05_tfw_item_distribution_by_age", "Full item response % by age group")
)
```

```{r}
#| label: tfw-item-age-plot
#| fig-height: 6
#| fig-cap: "Heatmap of % agree on focus items by age group."

if (nrow(item_age_agree) > 0) {
  ggplot(item_age_agree, aes(x = `Age group`, y = item, fill = agree_pct)) +
    geom_tile(colour = "white") +
    geom_text(aes(label = paste0(agree_pct, "%")), size = 3) +
    scale_fill_gradient(low = "#e8f5e9", high = "#2e7d32", name = "% agree") +
    labs(title = "TfWQ item % agree by age group",
         x = "Age group", y = NULL, caption = src_cap()) +
    theme_report()
}
```

## Item-level percentage by job grade

```{r}
#| label: tfw-item-job-table

item_job_dist <- item_long |>
  filter(!is.na(job_grade), !is.na(response)) |>
  count(job_grade, item, response, name = "n") |>
  group_by(job_grade, item) |>
  mutate(group_n = sum(n), pct = round(100 * n / group_n, 1)) |>
  ungroup() |>
  rename(`Job grade` = job_grade)

item_job_agree <- item_long |>
  filter(!is.na(job_grade), !is.na(score)) |>
  group_by(job_grade, item) |>
  summarise(
    n = n(),
    agree_pct = round(100 * mean(agree, na.rm = TRUE), 1),
    .groups = "drop"
  ) |>
  rename(`Job grade` = job_grade)

htmltools::tagList(
  show_tbl(item_job_agree, "05_tfw_item_agree_by_job", "% agree by item and job grade"),
  show_tbl(item_job_dist, "05_tfw_item_distribution_by_job", "Full item response % by job grade")
)
```

```{r}
#| label: tfw-item-job-plot
#| fig-height: 6
#| fig-cap: "Heatmap of % agree on focus items by job grade."

if (nrow(item_job_agree) > 0) {
  ggplot(item_job_agree, aes(x = `Job grade`, y = item, fill = agree_pct)) +
    geom_tile(colour = "white") +
    geom_text(aes(label = paste0(agree_pct, "%")), size = 3) +
    scale_fill_gradient(low = "#e8f5e9", high = "#2e7d32", name = "% agree") +
    labs(title = "TfWQ item % agree by job grade",
         x = "Job grade", y = NULL, caption = src_cap()) +
    theme_report() +
    theme(axis.text.x = element_text(angle = 20, hjust = 1))
}
```

# 6. WHO-5 and Thriving from Work — category matrix and latent profiles

This section has two parts that should not be mixed:

1. A **descriptive dual-continuum matrix** that assigns people with observed cut-points. It is **not** a latent profile analysis.
2. A **joint latent profile analysis** that models WHO-5 and the **US-normed TfWQ T-score** **in the same mixture**. The number of classes is chosen from fit statistics and interpretability; it is **not** forced to 2 or 4.

## 6.1 Descriptive dual-continuum matrix (not LPA)

Each respondent is assigned using observed scores: **Poor WHO-5 (clinical cutoff ≤13)** versus **Adequate WHO-5 (14–25)**, crossed with **TfWQ T-score below versus at or above the US average (T = 50)**. This is a dual-continuum category matrix, not a model-based typology. Age and job-grade comparisons below show the **cell mix within each group** (row percentages). Small groups (for example 60+) should be read cautiously.

```{r}
#| label: desc-matrix

df <- df |>
  mutate(
    who5_bin = wellbeing_cat,
    tfw_bin = tfw_t_cat,
    desc_cell = case_when(
      who5 <= who5_clinical_cut & tfw_t <  tfw_t_cut ~ "Poor WHO-5 / Below US average",
      who5 <= who5_clinical_cut & tfw_t >= tfw_t_cut ~ "Poor WHO-5 / At or above US average",
      who5 >  who5_clinical_cut & tfw_t <  tfw_t_cut ~ "Adequate WHO-5 / Below US average",
      who5 >  who5_clinical_cut & tfw_t >= tfw_t_cut ~ "Adequate WHO-5 / At or above US average",
      TRUE ~ NA_character_
    ) |> factor(levels = names(matrix_fill))
  )

desc_matrix <- df |>
  filter(!is.na(who5_bin), !is.na(tfw_bin)) |>
  count(who5_bin, tfw_bin, name = "n") |>
  mutate(pct = round(100 * n / sum(n), 1)) |>
  select(`WHO-5` = who5_bin, `Thriving` = tfw_bin, n, pct)

desc_cell_stats <- df |>
  filter(!is.na(desc_cell)) |>
  group_by(desc_cell) |>
  summarise(
    n = n(),
    pct = round(100 * n() / n_total, 1),
    who5_mean = round(mean(who5, na.rm = TRUE), 2),
    tfw_mean = round(mean(tfw, na.rm = TRUE), 2),
    tfw_t_mean = round(mean(tfw_t, na.rm = TRUE), 2),
    .groups = "drop"
  ) |>
  rename(Cell = desc_cell)

htmltools::tagList(
  htmltools::tags$p(sprintf(
    "Thriving uses the Harvard US T-score lookup after linearly rescaling the 1–5 sum (8–40) onto the official 1–6 sum (8–48). T < %d is below the US validation-sample average. WHO-5 uses the clinical screening cutoff (poor wellbeing ≤ %d).",
    tfw_t_cut, who5_clinical_cut
  )),
  show_tbl(desc_matrix, "06_desc_2x2_counts", "Descriptive 2 × 2 category matrix (WHO-5 clinical cutoff × US T-score)"),
  show_tbl(desc_cell_stats, "06_desc_2x2_means", "Descriptive cell size and mean scores")
)
```

```{r}
#| label: desc-heatmap
#| fig-cap: "Descriptive 2 × 2 matrix of WHO-5 (clinical cutoff ≤13 vs 14–25) and TfWQ T-score (below vs at/above US average). Not a latent profile analysis."

if (nrow(desc_matrix) > 0) {
  ggplot(desc_matrix, aes(x = Thriving, y = `WHO-5`, fill = n)) +
    geom_tile(colour = "white", linewidth = 1) +
    geom_text(aes(label = paste0(n, "\n(", pct, "%)")), size = 5) +
    scale_fill_gradient(low = "#deebf7", high = "#08519c") +
    labs(title = "Descriptive WHO-5 × Thriving category matrix",
         x = "Thriving from Work (US T-score vs average)",
         y = "WHO-5 (clinical cutoff ≤13 vs 14–25)",
         fill = "Count",
         caption = src_cap()) +
    theme_report() +
    theme(axis.text.x = element_text(angle = 15, hjust = 1)) +
    coord_fixed()
}
```

```{r}
#| label: desc-scatter
#| fig-cap: "WHO-5 versus Thriving scores coloured by the descriptive 2 × 2 cell."

if (n_total > 0) {
  ggplot(df, aes(x = who5, y = tfw_t, colour = desc_cell)) +
    geom_point(alpha = 0.75, size = 2.4, na.rm = TRUE) +
    geom_vline(xintercept = who5_clinical_cut + 0.5, linetype = "dashed", colour = "grey50") +
    geom_hline(yintercept = tfw_t_cut, linetype = "dashed", colour = "grey50") +
    scale_colour_manual(values = matrix_fill, drop = FALSE) +
    labs(title = "WHO-5 vs Thriving T-score by descriptive category",
         x = "WHO-5 score (0–25)",
         y = "Thriving from Work US T-score",
         colour = "Descriptive cell",
         caption = src_cap()) +
    theme_report() +
    theme(legend.position = "bottom", legend.title = element_text(size = 9)) +
    guides(colour = guide_legend(ncol = 2))
}
```

### Compare by age group

```{r}
#| label: desc-by-age-table

desc_by_age <- cat_by_group(df, age, desc_cell) |>
  rename(`Age group` = age, Cell = desc_cell)

show_tbl(desc_by_age, "06_desc_2x2_by_age", "Descriptive 2 × 2 cell by age group")
```

```{r}
#| label: desc-by-age-plot
#| fig-height: 5.5
#| fig-cap: "Descriptive 2 × 2 cell mix within each age group."

if (nrow(desc_by_age) > 0) {
  ggplot(desc_by_age, aes(x = `Age group`, y = n / group_n, fill = Cell)) +
    geom_col(position = "stack") +
    geom_text(aes(label = ifelse(pct >= 8, paste0(pct, "%"), "")),
              position = position_stack(vjust = 0.5), size = 3, colour = "white") +
    scale_y_continuous(labels = percent_format()) +
    scale_fill_manual(values = matrix_fill, drop = FALSE) +
    labs(title = "Descriptive 2 × 2 cell by age group",
         x = "Age group", y = "Percentage within age group",
         fill = "Cell", caption = src_cap()) +
    theme_report() +
    theme(legend.position = "bottom", legend.title = element_text(size = 9)) +
    guides(fill = guide_legend(ncol = 2, byrow = TRUE))
}
```

### Compare by job grade

```{r}
#| label: desc-by-job-table

desc_by_job <- cat_by_group(df, job_grade, desc_cell) |>
  rename(`Job grade` = job_grade, Cell = desc_cell)

show_tbl(desc_by_job, "06_desc_2x2_by_job", "Descriptive 2 × 2 cell by job grade")
```

```{r}
#| label: desc-by-job-plot
#| fig-height: 5.5
#| fig-cap: "Descriptive 2 × 2 cell mix within each job grade."

if (nrow(desc_by_job) > 0) {
  ggplot(desc_by_job, aes(x = fct_rev(`Job grade`), y = n / group_n, fill = Cell)) +
    geom_col(position = "stack") +
    geom_text(aes(label = ifelse(pct >= 8, paste0(pct, "%"), "")),
              position = position_stack(vjust = 0.5), size = 3, colour = "white") +
    coord_flip() +
    scale_y_continuous(labels = percent_format()) +
    scale_fill_manual(values = matrix_fill, drop = FALSE) +
    labs(title = "Descriptive 2 × 2 cell by job grade",
         x = NULL, y = "Percentage within job grade",
         fill = "Cell", caption = src_cap()) +
    theme_report() +
    theme(legend.position = "bottom", legend.title = element_text(size = 9)) +
    guides(fill = guide_legend(ncol = 2, byrow = TRUE))
}
```

## 6.2 Joint latent profile analysis

WHO-5 total and the **US-normed TfWQ T-score** are entered **together** as two continuous indicators (standardised so both scales contribute equally). Gaussian mixtures are estimated with `mclust` for **k = 1–5** under four covariance structures used in applied LPA:

- **EEI** — equal variances, covariances fixed at 0 (conditional independence)
- **VVI** — class-varying variances, covariances fixed at 0
- **EEE** — equal covariance matrix
- **VVV** — unconstrained covariance

k is **not** locked at 2 or 4. Among k ≥ 2 with smallest class ≥ 5%, the selected model is the **lowest ICL** with entropy ≥ 0.80 (falling back to entropy ≥ 0.60 if needed). ICL is used rather than BIC alone because BIC on two strongly related indicators often keeps splitting a single diagonal cloud into many ordered slices that are not distinct qualitative profiles.

`mclust` BIC is **higher = better**, which is the opposite of Mplus and most LPA papers. The table reports **conventional BIC / AIC / SABIC / ICL (lower = better)** and keeps mclust BIC for reference. The enumeration table still shows the BIC-best model so a competing solution can be inspected.

A 2 × 2 LPA reading (Low/Low, Low/High, High/Low, High/High) is used **only if** the selected solution has four classes whose means actually form those four combinations with usable sizes.

```{r}
#| label: lpa-fit

lpa <- fit_joint_lpa(df$who5, df$tfw_t)

df <- df |>
  mutate(
    lpa_id = lpa$class_id,
    lpa_class = lpa$class_lab
  )

lpa_enum_tbl <- lpa$enum
if (nrow(lpa_enum_tbl) > 0) {
  lpa_enum_tbl <- lpa_enum_tbl |>
    arrange(BIC, k, Model) |>
    mutate(
      candidate = if_else(candidate, "Yes", "No"),
      selected = if_else(selected, "Selected", ""),
      bic_best = if_else(bic_best, "BIC-best", "")
    )
}

bic_best_row <- if (nrow(lpa$enum) > 0) lpa$enum |> filter(bic_best) else tibble()
lpa_competing_note <- if (
  nrow(bic_best_row) == 1 &&
  !is.null(lpa$selected) &&
  !(identical(bic_best_row$Model, lpa$selected$Model) && identical(bic_best_row$k, lpa$selected$k))
) {
  why_not <- character()
  if (isTRUE(bic_best_row$smallest_pct < 5)) {
    why_not <- c(why_not, sprintf(
      "smallest class is only %.1f%% (n = %d), below the 5%% screen",
      bic_best_row$smallest_pct, bic_best_row$smallest_n
    ))
  }
  if (isTRUE(bic_best_row$entropy < 0.80)) {
    why_not <- c(why_not, sprintf("entropy is %.3f (below 0.80)", bic_best_row$entropy))
  }
  if (isTRUE(bic_best_row$ICL > lpa$selected$ICL)) {
    why_not <- c(why_not, "ICL is worse than the selected model")
  }
  if (length(why_not) == 0) why_not <- "it did not meet the selection screens"
  sprintf(
    "BIC-best model (not selected): %s with k = %d (BIC = %.1f, ICL = %.1f, entropy = %.3f, smallest class n = %d, %.1f%%). It was not selected because %s.",
    bic_best_row$Model, bic_best_row$k, bic_best_row$BIC, bic_best_row$ICL,
    bic_best_row$entropy, bic_best_row$smallest_n, bic_best_row$smallest_pct,
    paste(why_not, collapse = "; ")
  )
} else {
  NULL
}

lpa_selected_tbl <- if (!is.null(lpa$selected) && nrow(lpa$selected) == 1) {
  lpa$selected |>
    transmute(
      Model,
      k,
      npar,
      BIC,
      AIC,
      SABIC,
      ICL,
      entropy,
      AvePP,
      smallest_n,
      smallest_pct,
      Selection = lpa$reason
    )
} else {
  tibble(Note = lpa$reason)
}

lpa_class_stats <- df |>
  filter(!is.na(lpa_class)) |>
  group_by(lpa_class) |>
  summarise(
    n = n(),
    pct = round(100 * n() / lpa$n, 1),
    who5_mean = round(mean(who5, na.rm = TRUE), 2),
    who5_sd = round(sd(who5, na.rm = TRUE), 2),
    tfw_t_mean = round(mean(tfw_t, na.rm = TRUE), 2),
    tfw_t_sd = round(sd(tfw_t, na.rm = TRUE), 2),
    tfw_mean = round(mean(tfw, na.rm = TRUE), 2),
    .groups = "drop"
  ) |>
  rename(Profile = lpa_class)

lpa_k2x2_note <- if (isTRUE(lpa$looks_2x2)) {
  "The selected 4-class solution’s means correspond to the four Low/High combinations of WHO-5 and thriving, so a 2 × 2 LPA interpretation is reasonable here."
} else if (!is.null(lpa$selected) && isTRUE(lpa$selected$k == 4)) {
  "A 4-class model was selected, but class means do not form a clean Low/Low, Low/High, High/Low, High/High pattern. The 2 × 2 LPA interpretation is not used."
} else {
  "The selected solution is not a 4-class 2 × 2. That is expected when WHO-5 and thriving are strongly related: the data more often support 2–3 profiles (a large ‘doing well’ group plus smaller lower groups) than four balanced cells."
}

htmltools::tagList(
  htmltools::tags$p(lpa$reason),
  htmltools::tags$p(lpa_k2x2_note),
  if (!is.null(lpa_competing_note)) htmltools::tags$p(lpa_competing_note),
  if (nrow(lpa_enum_tbl) > 0) {
    show_tbl(
      lpa_enum_tbl,
      "06_lpa_enumeration",
      "Joint LPA enumeration (conventional BIC/AIC/SABIC/ICL: lower is better; mclust BIC: higher is better)"
    )
  },
  show_tbl(lpa_selected_tbl, "06_lpa_selected", "Selected joint LPA solution"),
  if (nrow(lpa_class_stats) > 0) {
    show_tbl(lpa_class_stats, "06_lpa_class_means", "Selected profile size and mean scores (WHO-5 raw; TfWQ US T-score)")
  }
)
```

```{r}
#| label: lpa-bic-plot
#| fig-cap: "Conventional BIC by number of classes and covariance structure (lower is better). Open circle = selected (ICL/entropy); triangle = BIC-best if different."

if (nrow(lpa$enum) > 0) {
  sel <- lpa$enum |> filter(selected)
  bb  <- lpa$enum |> filter(bic_best, !selected)
  ggplot(lpa$enum, aes(x = k, y = BIC, colour = Model, group = Model)) +
    geom_line(linewidth = 0.8) +
    geom_point(size = 2.2) +
    geom_point(data = sel, size = 5, shape = 21, fill = "white", stroke = 1.2, colour = "black") +
    {if (nrow(bb) > 0) geom_point(data = bb, size = 4, shape = 17, colour = "black") else NULL} +
    scale_x_continuous(breaks = sort(unique(lpa$enum$k))) +
    labs(title = "Joint LPA: conventional BIC by k and model",
         x = "Number of classes (k)",
         y = "Conventional BIC (lower is better)",
         colour = "Covariance",
         caption = src_cap()) +
    theme_report() +
    theme(legend.position = "bottom")
}
```

```{r}
#| label: lpa-scatter
#| fig-cap: "WHO-5 versus US-normed Thriving T-score coloured by joint LPA class."

if (n_total > 0 && any(!is.na(df$lpa_class))) {
  k <- nlevels(df$lpa_class)
  cols <- setNames(lpa_palette[seq_len(k)], levels(df$lpa_class))
  ggplot(df, aes(x = who5, y = tfw_t, colour = lpa_class)) +
    geom_point(alpha = 0.75, size = 2.4, na.rm = TRUE) +
    geom_hline(yintercept = tfw_t_cut, linetype = "dashed", colour = "grey50") +
    scale_colour_manual(values = cols, drop = FALSE, na.translate = FALSE) +
    labs(title = "WHO-5 vs Thriving T-score by joint LPA class",
         x = "WHO-5 score (0–25)",
         y = "Thriving from Work US T-score",
         colour = "LPA profile",
         caption = paste0(src_cap(), " · Dashed line: US average (T = 50)")) +
    theme_report() +
    theme(legend.position = "bottom", legend.title = element_text(size = 9)) +
    guides(colour = guide_legend(ncol = 2, byrow = TRUE))
}
```

```{r}
#| label: lpa-profile-means-plot
#| fig-width: 9
#| fig-height: 5.5
#| fig-cap: "Mean WHO-5 (percent of maximum) and thriving T-score (percent of US average) in each joint LPA profile."

if (nrow(lpa_class_stats) > 0) {
  wrap_lab <- function(x, width = 18) {
    vapply(x, function(s) paste(strwrap(s, width = width), collapse = "\n"), character(1))
  }
  lpa_class_stats |>
    mutate(
      Profile = factor(wrap_lab(as.character(Profile)), levels = wrap_lab(levels(df$lpa_class)))
    ) |>
    transmute(
      Profile,
      `WHO-5 (% of 25)` = 100 * who5_mean / 25,
      `Thriving (% of US avg)` = 100 * tfw_t_mean / tfw_t_cut
    ) |>
    pivot_longer(-Profile, names_to = "Scale", values_to = "pct") |>
    ggplot(aes(x = Profile, y = pct, fill = Scale)) +
    geom_col(position = position_dodge(width = 0.75), width = 0.7) +
    geom_hline(yintercept = 100, linetype = "dashed", colour = "grey40") +
    geom_text(aes(label = sprintf("%.0f%%", pct)),
              position = position_dodge(width = 0.75), vjust = -0.4, size = 3) +
    scale_fill_manual(values = c("WHO-5 (% of 25)" = "#4E79A7", "Thriving (% of US avg)" = "#59A14F")) +
    labs(title = "Joint LPA profile means",
         x = NULL, y = "Percent", fill = NULL,
         caption = paste0(src_cap(), " · WHO-5 is % of 25; thriving is % of US average T-score (50 = 100%)")) +
    theme_report() +
    theme(
      legend.position = "bottom",
      axis.text.x = element_text(size = 10, lineheight = 1.05)
    ) +
    scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.12)))
}
```

Class membership is assigned after the joint model is selected. Age and job grade are **not** used to estimate classes; the tables and charts below are descriptive only. Percentages are within each age group or job grade. The smaller LPA class is typically a few percent of the sample, so some cells will have very small n.

### Compare by age group

```{r}
#| label: lpa-by-age-table

lpa_by_age <- cat_by_group(df, age, lpa_class) |>
  rename(`Age group` = age, Profile = lpa_class)

show_tbl(lpa_by_age, "06_lpa_class_by_age", "Joint LPA class by age group (descriptive, after classification)")
```

```{r}
#| label: lpa-by-age-plot
#| fig-cap: "Joint LPA class mix within each age group."

if (nrow(lpa_by_age) > 0 && any(!is.na(df$lpa_class))) {
  k <- nlevels(df$lpa_class)
  cols <- setNames(lpa_palette[seq_len(k)], levels(df$lpa_class))
  ggplot(lpa_by_age, aes(x = `Age group`, y = n / group_n, fill = Profile)) +
    geom_col(position = "stack") +
    geom_text(aes(label = ifelse(pct >= 8, paste0(pct, "%"), "")),
              position = position_stack(vjust = 0.5), size = 3, colour = "white") +
    scale_y_continuous(labels = percent_format()) +
    scale_fill_manual(values = cols, drop = FALSE) +
    labs(title = "Joint LPA class by age group",
         x = "Age group", y = "Percentage within age group",
         fill = "LPA profile", caption = src_cap()) +
    theme_report() +
    theme(legend.position = "bottom", legend.title = element_text(size = 9)) +
    guides(fill = guide_legend(ncol = 2, byrow = TRUE))
}
```

### Compare by job grade

```{r}
#| label: lpa-by-job-table

lpa_by_job <- cat_by_group(df, job_grade, lpa_class) |>
  rename(`Job grade` = job_grade, Profile = lpa_class)

show_tbl(lpa_by_job, "06_lpa_class_by_job", "Joint LPA class by job grade (descriptive, after classification)")
```

```{r}
#| label: lpa-by-job-plot
#| fig-cap: "Joint LPA class mix within each job grade."

if (nrow(lpa_by_job) > 0 && any(!is.na(df$lpa_class))) {
  k <- nlevels(df$lpa_class)
  cols <- setNames(lpa_palette[seq_len(k)], levels(df$lpa_class))
  ggplot(lpa_by_job, aes(x = fct_rev(`Job grade`), y = n / group_n, fill = Profile)) +
    geom_col(position = "stack") +
    geom_text(aes(label = ifelse(pct >= 8, paste0(pct, "%"), "")),
              position = position_stack(vjust = 0.5), size = 3, colour = "white") +
    coord_flip() +
    scale_y_continuous(labels = percent_format()) +
    scale_fill_manual(values = cols, drop = FALSE) +
    labs(title = "Joint LPA class by job grade",
         x = NULL, y = "Percentage within job grade",
         fill = "LPA profile", caption = src_cap()) +
    theme_report() +
    theme(legend.position = "bottom", legend.title = element_text(size = 9)) +
    guides(fill = guide_legend(ncol = 2, byrow = TRUE))
}
```

# 7. Item-level latent profile analysis (all scored items)

Section 6 modelled **two scale totals** (WHO-5 and the TfWQ T-score). This section instead fits one joint mixture to **all 15 scored item responses**: WHO-5 items 1–5, peer support items 1–2, and TfWQ short-form items 3–10. Items are standardised so each contributes equally. Class number and covariance structure are chosen with the same ICL / entropy / size screens as Section 6. Age and job grade are not used to estimate classes.

```{r}
#| label: lpa7-fit

parse_ans <- function(x) as.integer(str_extract(as.character(x), "^\\d+"))

lpa7_item_df <- tibble(
  p1_1  = parse_ans(df[["answers.part1-1"]]),
  p1_2  = parse_ans(df[["answers.part1-2"]]),
  p1_3  = parse_ans(df[["answers.part1-3"]]),
  p1_4  = parse_ans(df[["answers.part1-4"]]),
  p1_5  = parse_ans(df[["answers.part1-5"]]),
  p2_1  = parse_ans(df[["answers.part2-1"]]),
  p2_2  = parse_ans(df[["answers.part2-2"]]),
  p2_3  = parse_ans(df[["answers.part2-3"]]),
  p2_4  = parse_ans(df[["answers.part2-4"]]),
  p2_5  = parse_ans(df[["answers.part2-5"]]),
  p2_6  = parse_ans(df[["answers.part2-6"]]),
  p2_7  = parse_ans(df[["answers.part2-7"]]),
  p2_8  = parse_ans(df[["answers.part2-8"]]),
  p2_9  = parse_ans(df[["answers.part2-9"]]),
  p2_10 = parse_ans(df[["answers.part2-10"]])
)
names(lpa7_item_df) <- unname(lpa_all_item_lab)

lpa7 <- fit_lpa_matrix(as.matrix(lpa7_item_df))

lpa7_class <- rep(NA_character_, nrow(df))
if (!is.null(lpa7$fit) && !is.null(lpa7$selected)) {
  ok <- lpa7$ok
  cls <- lpa7$class_id[ok]
  labs_ok <- lpa_item_class_labels(df$who5[ok], df$tfw_t[ok], df$peer[ok], cls)
  z_overall <- rowMeans(scale(as.matrix(lpa7_item_df)[ok, , drop = FALSE]), na.rm = TRUE)
  ov_m <- tapply(z_overall, cls, mean, na.rm = TRUE)
  lab_by_id <- tapply(labs_ok, cls, function(v) v[1])
  lab_levels <- unname(lab_by_id[order(ov_m)])
  lpa7_class[ok] <- labs_ok
  lpa7_class <- factor(lpa7_class, levels = lab_levels)
} else {
  lpa7_class <- factor(lpa7_class)
}

df <- df |> mutate(lpa7_class = lpa7_class)

lpa7_enum_tbl <- lpa7$enum
if (nrow(lpa7_enum_tbl) > 0) {
  lpa7_enum_tbl <- lpa7_enum_tbl |>
    arrange(BIC, k, Model) |>
    mutate(
      candidate = if_else(candidate, "Yes", "No"),
      selected = if_else(selected, "Selected", ""),
      bic_best = if_else(bic_best, "BIC-best", "")
    )
}

lpa7_bic_best_row <- if (nrow(lpa7$enum) > 0) lpa7$enum |> filter(bic_best) else tibble()
lpa7_competing_note <- if (
  nrow(lpa7_bic_best_row) == 1 &&
  !is.null(lpa7$selected) &&
  !(identical(lpa7_bic_best_row$Model, lpa7$selected$Model) && identical(lpa7_bic_best_row$k, lpa7$selected$k))
) {
  why_not <- character()
  if (isTRUE(lpa7_bic_best_row$smallest_pct < 5)) {
    why_not <- c(why_not, sprintf(
      "smallest class is only %.1f%% (n = %d), below the 5%% screen",
      lpa7_bic_best_row$smallest_pct, lpa7_bic_best_row$smallest_n
    ))
  }
  if (isTRUE(lpa7_bic_best_row$entropy < 0.80)) {
    why_not <- c(why_not, sprintf("entropy is %.3f (below 0.80)", lpa7_bic_best_row$entropy))
  }
  if (isTRUE(lpa7_bic_best_row$ICL > lpa7$selected$ICL)) {
    why_not <- c(why_not, "ICL is worse than the selected model")
  }
  if (length(why_not) == 0) why_not <- "it did not meet the selection screens"
  sprintf(
    "BIC-best model (not selected): %s with k = %d (BIC = %.1f, ICL = %.1f, entropy = %.3f, smallest class n = %d, %.1f%%). It was not selected because %s.",
    lpa7_bic_best_row$Model, lpa7_bic_best_row$k, lpa7_bic_best_row$BIC, lpa7_bic_best_row$ICL,
    lpa7_bic_best_row$entropy, lpa7_bic_best_row$smallest_n, lpa7_bic_best_row$smallest_pct,
    paste(why_not, collapse = "; ")
  )
} else {
  NULL
}

lpa7_selected_tbl <- if (!is.null(lpa7$selected) && nrow(lpa7$selected) == 1) {
  lpa7$selected |>
    transmute(
      Model, k, npar, BIC, AIC, SABIC, ICL, entropy, AvePP, smallest_n, smallest_pct,
      Selection = lpa7$reason
    )
} else {
  tibble(Note = lpa7$reason)
}

lpa7_class_stats <- df |>
  filter(!is.na(lpa7_class)) |>
  group_by(lpa7_class) |>
  summarise(
    n = n(),
    pct = round(100 * n() / lpa7$n, 1),
    who5_mean = round(mean(who5, na.rm = TRUE), 2),
    tfw_t_mean = round(mean(tfw_t, na.rm = TRUE), 2),
    tfw_mean = round(mean(tfw, na.rm = TRUE), 2),
    peer_mean = round(mean(peer, na.rm = TRUE), 2),
    .groups = "drop"
  ) |>
  rename(Profile = lpa7_class)

lpa7_item_means <- if (any(!is.na(df$lpa7_class))) {
  bind_cols(lpa7_item_df, tibble(Profile = df$lpa7_class)) |>
    filter(!is.na(Profile)) |>
    pivot_longer(-Profile, names_to = "Item", values_to = "score") |>
    group_by(Profile, Item) |>
    summarise(mean = round(mean(score, na.rm = TRUE), 2), .groups = "drop") |>
    mutate(Item = factor(Item, levels = unname(lpa_all_item_lab))) |>
    arrange(Item, Profile)
} else {
  tibble()
}

lpa7_item_wide <- if (nrow(lpa7_item_means) > 0) {
  lpa7_item_means |>
    mutate(P = paste0("P", as.integer(Profile))) |>
    select(Item, P, mean) |>
    pivot_wider(names_from = P, values_from = mean)
} else {
  tibble()
}

htmltools::tagList(
  htmltools::tags$p(sprintf(
    "Complete cases for the 15-item LPA: n = %d of %d valid submissions (%.1f%%). Items are standardised inside the mixture. Unconstrained (VVV) models may not estimate with 15 indicators; those rows are simply omitted.",
    lpa7$n, n_total, if (n_total > 0) 100 * lpa7$n / n_total else 0
  )),
  htmltools::tags$p(lpa7$reason),
  if (!is.null(lpa7_competing_note)) htmltools::tags$p(lpa7_competing_note),
  if (nrow(lpa7_enum_tbl) > 0) {
    show_tbl(
      lpa7_enum_tbl,
      "07_lpa_enumeration",
      "Item-level LPA enumeration (conventional BIC/AIC/SABIC/ICL: lower is better; mclust BIC: higher is better)"
    )
  },
  show_tbl(lpa7_selected_tbl, "07_lpa_selected", "Selected item-level LPA solution"),
  if (nrow(lpa7_class_stats) > 0) {
    show_tbl(
      lpa7_class_stats,
      "07_lpa_class_means",
      "Selected profile size and scale means (WHO-5 raw; TfWQ US T-score; peer support 2–10)"
    )
  },
  if (nrow(lpa7_item_wide) > 0) {
    show_tbl(lpa7_item_wide, "07_lpa_item_means", "Mean item score by profile (raw item metric)")
  }
)
```

```{r}
#| label: lpa7-bic-plot
#| fig-cap: "Item-level LPA: conventional BIC by number of classes and covariance structure (lower is better). Open circle = selected (ICL/entropy); triangle = BIC-best if different."

if (nrow(lpa7$enum) > 0) {
  sel <- lpa7$enum |> filter(selected)
  bb  <- lpa7$enum |> filter(bic_best, !selected)
  ggplot(lpa7$enum, aes(x = k, y = BIC, colour = Model, group = Model)) +
    geom_line(linewidth = 0.8) +
    geom_point(size = 2.2) +
    geom_point(data = sel, size = 5, shape = 21, fill = "white", stroke = 1.2, colour = "black") +
    {if (nrow(bb) > 0) geom_point(data = bb, size = 4, shape = 17, colour = "black") else NULL} +
    scale_x_continuous(breaks = sort(unique(lpa7$enum$k))) +
    labs(title = "Item-level LPA: conventional BIC by k and model",
         x = "Number of classes (k)",
         y = "Conventional BIC (lower is better)",
         colour = "Covariance",
         caption = src_cap()) +
    theme_report() +
    theme(legend.position = "bottom")
}
```

```{r}
#| label: lpa7-profile-plot
#| fig-width: 9
#| fig-height: 7
#| fig-cap: "Standardised item means (z) by item-level LPA profile. Zero is the sample mean on that item."

if (nrow(lpa7_item_means) > 0 && any(!is.na(df$lpa7_class))) {
  k <- nlevels(df$lpa7_class)
  cols <- setNames(rep(lpa_palette, length.out = k), levels(df$lpa7_class))
  z_items <- as.data.frame(scale(as.matrix(lpa7_item_df)))
  names(z_items) <- unname(lpa_all_item_lab)
  z_long <- bind_cols(z_items, tibble(Profile = df$lpa7_class)) |>
    filter(!is.na(Profile)) |>
    pivot_longer(-Profile, names_to = "Item", values_to = "z") |>
    group_by(Profile, Item) |>
    summarise(z = mean(z, na.rm = TRUE), .groups = "drop") |>
    mutate(Item = factor(Item, levels = unname(lpa_all_item_lab)))
  ggplot(z_long, aes(x = z, y = fct_rev(Item), colour = Profile, group = Profile)) +
    geom_vline(xintercept = 0, linetype = "dashed", colour = "grey50") +
    geom_line() +
    geom_point(size = 2) +
    scale_colour_manual(values = cols, drop = FALSE) +
    labs(title = "Item-level LPA profiles (standardised means)",
         x = "Mean z-score (0 = sample mean)",
         y = NULL,
         colour = "LPA profile",
         caption = src_cap()) +
    theme_report() +
    theme(legend.position = "bottom", legend.title = element_text(size = 9)) +
    guides(colour = guide_legend(ncol = 2, byrow = TRUE))
}
```

Class membership is assigned after the item-level model is selected. Age and job grade are **not** used to estimate classes; the tables and charts below are descriptive only.

### Compare by age group

```{r}
#| label: lpa7-by-age-table

lpa7_by_age <- cat_by_group(df, age, lpa7_class) |>
  rename(`Age group` = age, Profile = lpa7_class)

show_tbl(lpa7_by_age, "07_lpa_class_by_age", "Item-level LPA class by age group (descriptive, after classification)")
```

```{r}
#| label: lpa7-by-age-plot
#| fig-cap: "Item-level LPA class mix within each age group."

if (nrow(lpa7_by_age) > 0 && any(!is.na(df$lpa7_class))) {
  k <- nlevels(df$lpa7_class)
  cols <- setNames(rep(lpa_palette, length.out = k), levels(df$lpa7_class))
  ggplot(lpa7_by_age, aes(x = `Age group`, y = n / group_n, fill = Profile)) +
    geom_col(position = "stack") +
    geom_text(aes(label = ifelse(pct >= 8, paste0(pct, "%"), "")),
              position = position_stack(vjust = 0.5), size = 3, colour = "white") +
    scale_y_continuous(labels = percent_format()) +
    scale_fill_manual(values = cols, drop = FALSE) +
    labs(title = "Item-level LPA class by age group",
         x = "Age group", y = "Percentage within age group",
         fill = "LPA profile", caption = src_cap()) +
    theme_report() +
    theme(legend.position = "bottom", legend.title = element_text(size = 9)) +
    guides(fill = guide_legend(ncol = 2, byrow = TRUE))
}
```

### Compare by job grade

```{r}
#| label: lpa7-by-job-table

lpa7_by_job <- cat_by_group(df, job_grade, lpa7_class) |>
  rename(`Job grade` = job_grade, Profile = lpa7_class)

show_tbl(lpa7_by_job, "07_lpa_class_by_job", "Item-level LPA class by job grade (descriptive, after classification)")
```

```{r}
#| label: lpa7-by-job-plot
#| fig-cap: "Item-level LPA class mix within each job grade."

if (nrow(lpa7_by_job) > 0 && any(!is.na(df$lpa7_class))) {
  k <- nlevels(df$lpa7_class)
  cols <- setNames(rep(lpa_palette, length.out = k), levels(df$lpa7_class))
  ggplot(lpa7_by_job, aes(x = fct_rev(`Job grade`), y = n / group_n, fill = Profile)) +
    geom_col(position = "stack") +
    geom_text(aes(label = ifelse(pct >= 8, paste0(pct, "%"), "")),
              position = position_stack(vjust = 0.5), size = 3, colour = "white") +
    coord_flip() +
    scale_y_continuous(labels = percent_format()) +
    scale_fill_manual(values = cols, drop = FALSE) +
    labs(title = "Item-level LPA class by job grade",
         x = NULL, y = "Percentage within job grade",
         fill = "LPA profile", caption = src_cap()) +
    theme_report() +
    theme(legend.position = "bottom", legend.title = element_text(size = 9)) +
    guides(fill = guide_legend(ncol = 2, byrow = TRUE))
}
```

# Download all tables

```{r}
#| label: download-all-tables

if (length(.table_store) > 0) {
  xlsx_name <- "emotion_twister_tables.xlsx"
  writexl::write_xlsx(.table_store, xlsx_name)
  htmltools::tagList(
    htmltools::tags$p("Combined workbook of every results table in this report:"),
    htmltools::tags$p(
      htmltools::tags$a(
        href = xlsx_name,
        download = xlsx_name,
        class = "btn-dl",
        "Download all tables (Excel)"
      )
    )
  )
}
```

# Notes

- Configured organisation, `use_all_dates`, optional date range / `include_windows`, and `include_hk_forms` are set in the **Configuration** chunk at the top of this file (or by `_company_config.R` for company batch renders).
- Internal `@bokss.org.hk` emails, duplicate emails (first submission kept), Forms attention-check failures (not “一般”), and **Other** on job grade, gender, or education are excluded.
- When `include_hk_forms` is TRUE, the Microsoft Forms file 全港職場精神健康調查(1-107).xlsx is merged with the live survey export. Forms emails are anonymous, so those rows cannot be de-duplicated against the API. Forms job-grade Other write-ins **Director** and **老闆** are recoded to Senior-level. Retired, blank Other, and other non-grade write-ins stay excluded. Company-specific reports set `include_hk_forms` to FALSE.
- WHO-5 categories use the clinical screening cutoff: Poor wellbeing (raw score ≤13) versus Adequate wellbeing (14–25).
- TfWQ item labels for items 4, 5, 6, 9 and 10 assume the Harvard short-form order for Part 2 items 3–10.
- TfWQ totals are collected on a 5-point agreement scale (8–40), linearly rescaled to the official 1–6 short-form metric (8–48), then converted with the Harvard US T-score lookup (Gundersen, Peters, Neidlinger & Wagner, Scoring Guide, May 2025). T = 50 is the US validation-sample average. The original items use agreement labels, not the official Never–Always frequency labels, so the T-score is an approximation.
- The Section 6 **2 × 2 matrix is descriptive** (WHO-5 clinical cutoff ≤13 vs 14–25, crossed with TfWQ T < 50 vs T ≥ 50). It is not a latent profile analysis. Age and job-grade charts for both the matrix and the LPA are within-group percentages.
- Joint LPA (Section 6) uses `mclust` Gaussian mixtures on standardised WHO-5 and the US-normed TfWQ T-score together. k is chosen from ICL (lower is better) among solutions with smallest class ≥ 5% and entropy ≥ 0.80 — not forced to 2 or 4. Conventional BIC/AIC/SABIC are still tabulated. `mclust` BIC has the opposite sign to Mplus/literature. Bootstrap likelihood-ratio tests are not computed. Small classes (<5%) should be treated cautiously.
- Section 7 is a separate item-level LPA on all 15 scored items (WHO-5 1–5, peer support 1–2, TfWQ 3–10), standardised, with the same selection screens as Section 6. It is not a replacement for the two-indicator joint LPA.
